\textbf{COMP0085 Summative Assignment}

### 2023-01-01 submission.tex
update figures and report
split out em and binary approximation model
add new python files to report

@@

@@

%Optimising the parameters $\{a, b\}$, and $\alpha^2$ in turn, will cause some $\alpha_i^2$ to diverge, the number of remaining $\alpha_i^2$ provide our determination for the value of $K$. This is automatic relevance determination through factor analysis.

\newpage
The Python code for variational Bayes:
\lstinputlisting[language=Python]{src/models/variational_bayes.py}

>>>>

\newpage
The Python code for an abstract binary latent factor model approximation:
\lstinputlisting[language=Python]{src/models/binary_latent_factor_model_approximation.py}

@@

\newpage
The Python code for expectation maximisation:
\lstinputlisting[language=Python]{src/expectation_maximisation.py}

@@

\newpage
\begin{figure}[h]
\centering
\begin{minipage}{.6\textwidth}
  \centering
\includegraphics[scale=0.15]{outputs/q4/b-latent-factors}
\caption{Learned Latent Factors}
\label{fig:}
\end{minipage}%
\begin{minipage}{.2\textwidth}
  \centering
\includegraphics[scale=0.11]{outputs/q4/b-alpha-trained}
\caption{Alpha values}
\label{fig:}
\end{minipage}
\end{figure}

\newpage
\begin{figure}[h]
\centering
\includegraphics[scale=0.8]{outputs/q4/b-free-energy}
\caption{Free Energy for different values of k}
\label{fig:}
\end{figure}

\newpage
The Python code for Variational Bayes:
\lstinputlisting[language=Python]{src/models/variational_bayes.py}
